Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-22 Manuscript/FLPhish(Trans).tex
algorithm update

\begin{algorithm}[t]
  \caption{Ensemble FL} %algorithm name
  \label{alg:system}
  \hspace*{0.02in} {\bf Input:} %the input of the algorithm
  the ensemble of clients $C$ with local dataset $d_i$, $i=1,2,3,...,u$; a central server $s$ with unlabeled dataset $D$; number of training iterations $T$; unlabeled batch size $n$;\\
  \hspace*{0.02in} {\bf Output:} %output of the algorithm
  \begin{algorithmic}[1]
    \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its local dataset $d_i$;
    \For{\textit{t=1,2,3,..,,T}}
      \State $s$ selects $D_t$ (containing $n$ samples) from $D$;
      \For{\textit{i=1,2,3,...,u}}
        \State $s \overset{D_{t}}{\rightarrow} c_{i}$;
        \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$;
        \State $c_i \overset{\mathbf{k_i^t}}{\rightarrow} s$;
      \EndFor
      \State $Y_t$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$;
      \State $\mathbf{M}$ = $ModelUpdate(Y_t, D_t, \mathbf{M})$;
    \EndFor \\
    \Return $\mathbf{M}$.
  \end{algorithmic}
\end{algorithm}
\begin{algorithm}[t]
  \caption{KnowledgeEnsemble} %algorithm name
  \label{alg:KnowledgeEnsemble}
  \hspace*{0.02in} {\bf Input:} %input of the algorithm
  the ensemble of ${\mathbf{k_i^t}}_{\left \{ i= 1,2,3,...,u \right \}}$; size of each client's local dataset ${e_i}_{\left \{ i= 1,2,3,...,u \right \}}$; the unlabeled dataset $D_t$ used in $t$th procedure; $\mathbf{\hat{y}^t}$ is the ensembled prediction of dataset $D_t$; $\mathbf{\hat{y}^t_l}$ denotes the prediction of the dataset $D_t$ made by $i$th client;\\
  \hspace*{0.02in} {\bf Output:} %output of the algorithm
  \begin{algorithmic}[1]
    \For{$l=1,2,3,...,n$ ($l=1,2,3,...,n$, denotes the data point in the unlabeled dataset)}
      \State $\mathbf{\hat{k}^t}$ $\gets$ $\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i$;
      \State $\mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t})$;
    \EndFor \\
    \Return $\mathbf{\hat{y}^t}$.
  \end{algorithmic}

@@

  \begin{algorithm}[t]
    \caption{Phishing Mechanism} 
    \hspace*{0.02in} {\bf Input:} 
    the ensemble of clients $C$ with local dataset $d_i$, $i=1,2,3,...,u$; a central server $s$ with unlabeled dataset $D$ and labeled dataset $B$; number of training iterations $T$; unlabeled batch size $n$;labeled batch size $m$.\\
    \hspace*{0.02in} {\bf Output:} 
    output result
    \begin{algorithmic}[1]
      \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its local dataset $d_i$.
      \For{\textit{t=1,2,3,..,,T}}
        \State $s$ selects $D_t$ (containing $n$ samples) from $D$ and $B_t$ (containing $m$ samples) from $B$.
        \For{\textit{i=1,2,3,...,u}}
          \State $s$ sends $D_t$ and $B_t$ to $c_i$.
          \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$ and $B_t$.
          \State $c_i$ sends $\mathbf{k_i^t}$ to $s$.
          \State $s$ calculates the accuracy $a_i^t$ of the predictions of $B_t$ made by $c_i$ in $t$th procedure.
          \If{$a_i^t > r_q$}
            \State $q_i = 1$.
            \For{\textit{j=i,i+1,i+2,...,u-1}}
              \State $(d,c,\mathbf{k^t},q,a^t)_j \gets (d,c,\mathbf{k^t},q,a^t)_{j-1}$.
            \EndFor
          \EndIf
        \EndFor
        \State $\mathbf{K_t}$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$.
        \State $\mathbf{M}$ = $ModelUpdate(\mathbf{K_t}, D_t, \mathbf{M})$.
      \EndFor
      \State\Return $\mathbf{M}$
    \end{algorithmic}
    \end{algorithm}

>>>>

\begin{algorithm}[t]
  \caption{Ensemble FL} %algorithm name
  \label{alg:system}
  \hspace*{0.02in} {\bf Input:} %the input of the algorithm
  each FL client $c_i$, $i=1,2,3,...,u$ with its local dataset $d_i$, $i=1,2,3,...,u$; an FL central server $s$ with the unlabeled dataset $D$ preserved by itself; number of the FL training iterations $T$; the size of unlabeled batch $n$ in each iteration;\\
  \hspace*{0.02in} {\bf Output:} %output of the algorithm
  \begin{algorithmic}[1]
    \State $\mathbf{m_i}$ $\gets$ each FL client $c_i$ trains a local model using its local dataset $d_i$ collected by itself;
    \For{\textit{t=1,2,3,..,,T}}
      \State $s$ selects $D_t$ (containing $n$ data samples) from $D$;
      \For{\textit{i=1,2,3,...,u}}
        \State $s \overset{D_{t}}{\rightarrow} c_{i}$;
        \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$;
        \State $c_i \overset{\mathbf{k_i^t}}{\rightarrow} s$;
      \EndFor
      \State $Y_t$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$;
      \State $\mathbf{M}$ = $ModelUpdate(Y_t, D_t, \mathbf{M})$;
    \EndFor \\
    \Return $\mathbf{M}$.
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
  \caption{KnowledgeEnsemble} %algorithm name
  \label{alg:KnowledgeEnsemble}
  \hspace*{0.02in} {\bf Input:} %input of the algorithm
  the ensemble of each client's prediction (`distilled knowledge') ${\mathbf{k_i^t}}_{\left \{ i= 1,2,3,...,u \right \}}$; the size of each client's local dataset ${e_i}_{\left \{ i= 1,2,3,...,u \right \}}$; the unlabeled dataset $D_t$ used in $t$th iteration; $\mathbf{\hat{y}^t}$ is the ensembled prediction of dataset $D_t$; $\mathbf{\hat{y}^t_l}$ denotes the prediction of the dataset $D_t$ made by $i$th client;\\
  \hspace*{0.02in} {\bf Output:} %output of the algorithm
  \begin{algorithmic}[1]
    \For{$l=1,2,3,...,n$ ($l=1,2,3,...,n$, denotes the data point in the unlabeled dataset)}
      \State $\mathbf{\hat{k}^t}$ $\gets$ $\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i$;
      \State $\mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t})$;
    \EndFor \\
    \Return $\mathbf{\hat{y}^t}$.
  \end{algorithmic}

@@

  \begin{algorithm}[t]
    \caption{Phishing Mechanism} 
    \hspace*{0.02in} {\bf Input:} 
    each FL client $c_i$, $i=1,2,3,...,u$ with its local dataset $d_i$, $i=1,2,3,...,u$; an FL central server $s$ with the unlabeled dataset $D$ and labeled dataset $B$ preserved by itself; the number of FL training iterations $T$; the size of the unlabeled batch $n$ used in each training iteration; the size of the labeled batch $m$ used in each training iteration.\\
    \hspace*{0.02in} {\bf Output:} 
    output result
    \begin{algorithmic}[1]
      \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its local dataset $d_i$.
      \For{\textit{t=1,2,3,..,,T}}
        \State $s$ selects $D_t$ (containing $n$ samples) from $D$ and $B_t$ (containing $m$ samples) from $B$.
        \For{\textit{i=1,2,3,...,u}}
          \State $s$ sends $D_t$ and $B_t$ to $c_i$.
          \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$ and $B_t$.
          \State $c_i$ sends $\mathbf{k_i^t}$ to $s$.
          \State $s$ calculates the accuracy $a_i^t$ of the predictions of $B_t$ made by $c_i$ in $t$th procedure.
          \If{$a_i^t > r_q$}
            \State $q_i = 1$.
            \For{\textit{j=i,i+1,i+2,...,u-1}}
              \State $(d,c,\mathbf{k^t},q,a^t)_j \gets (d,c,\mathbf{k^t},q,a^t)_{j-1}$.
            \EndFor
          \EndIf
        \EndFor
        \State $\mathbf{K_t}$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$.
        \State $\mathbf{M}$ = $ModelUpdate(\mathbf{K_t}, D_t, \mathbf{M})$.
      \EndFor
      \State\Return $\mathbf{M}$
    \end{algorithmic}
    \end{algorithm}
